Wireless service accounting based on Ethereum state channels - Master Thesis

### 2019-10-02 Paper.tex
Change title

\documentclass[12pt]{amsart}
%\usepackage{tweaklist}
\usepackage{cancel}
\usepackage{xspace}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{multicol}
\usepackage{subfig}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[a4paper,width=170mm,top=18mm,bottom=21mm,includeheadfoot]{geometry}
\usepackage{booktabs}
\usepackage{array}
\usepackage{verbatim}
\usepackage{caption}
% \usepackage{natbib}

@@

\title{ETH-Paid Internet Access\\ {\smaller \textbf{Master thesis}}}

@@

\begin{abstract}
  \begin{center}
    This document contains authors' ``\textit{Blockchain
      technologies master}''\footnote{UPC School
      of Professional \& Executive Development}
    final thesis. The project described in the document
    consists on a technological proof
    of concept of an internet access service consumption
    using a state channel smart contract as
    mean of payment. After a brief
    introduction, there's a first motivation of
    the use case included;
    in the following sections
    there's a detailed explanation of
    the architecture, implementation and
    security considerations;
    after that it is described a more
    general approach on using blockchain technologies
    and state channels in particular to provide
    mechanisms to reduce advanced wireless
    (i. e. 5G) services market friction between neutral host
    providers, virtual operators and operators
    licensing spectrum bands to states;
    guarantee transparency to consumers,
    and provide a fully GDPR compliant
    schema using a self-sovereign identity system.
  \end{center}
\end{abstract}

@@

As dynamic host configuration server for the wireless
network, dnsmasq was used.

iptables\cite{iptables} was used as a firewall running
inside the Raspberry; by default, it was configured to
drop all packet
forwarding traffic from users connected to the wireless
domain and at the same time to redirect all
forwarding traffic to Raspberry's HTTP port where a
captive portal was deployed.

Un resumen de sus especificaciones se da a continuación (véase tabla 1):
\begin{center}
%\begin{tabular} to 0.5\textwidth { | X[l] | X[r] | }
\begin{tabular}{ | m{0.125\textwidth} | m{0.3125\textwidth} | }
 \hline
 Especificaciones & Raspberry Pi 3 Modelo B \\
 \hline
 Procesador & Broadcom BCM2837, Cortex-A53 (ARMv8) 64-bit SoC @ 1,2 GHz \\
\hline
 RAM & 1 GB \\
\hline
 Conectividad & Wi-Fi 802.11 b/g/n (2,4 GHz) Bluetooth 4.1 Puerto Ethernet de hasta 100 Mbps \\
\hline
 Puertos & HDMI completo, 4 USB 2.0, MicroSD, CSI camera, DSI display \\
\hline
 Memoria & MicroSD \\
\hline
\end{tabular}
\newline
\end{center}
Tabla 1. Especificaciones de Raspberry Pi 3 Modelo B
%\newline
Aunque no se indica expresamente si es hardware libre (\textit{open hardware}) o con derechos de marca, en su página Web oficial explican que disponen de contratos de distribución y venta con dos empresas. Pero al mismo tiempo, cualquiera puede convertirse en revendedor o redistribuidor de las tarjetas Raspberry Pi [RaspberryPiBuy 19].

>>>>

\documentclass[12pt]{amsart}
%\usepackage{tweaklist}
\usepackage{cancel}
\usepackage{xspace}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{multicol}
\usepackage{subfig}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[a4paper,width=160mm,top=18mm,bottom=21mm,includeheadfoot]{geometry}
\usepackage{booktabs}
\usepackage{array}
\usepackage{verbatim}
\usepackage{caption}
% \usepackage{natbib}

@@

\title{Wireless service accounting based on Ethereum state channels
- Master Thesis}

@@

\begin{abstract}
  \begin{center}
    This document contains authors' ``\textit{Blockchain
      technologies master}''\footnote{UPC School
      of Professional \& Executive Development}
    final thesis. The project described in the document
    consists on a technological proof
    of concept of an internet access service consumption
    using a state channel smart contract as
    mean of payment. After a brief
    introduction, there's a first motivation of
    the use case included;
    in the following sections
    there's a detailed explanation of
    the architecture, implementation and
    security considerations;
    after that it is described a more
    general approach on using blockchain technologies
    and state channels in particular to provide
    mechanisms to reduce advanced wireless
    (i. e. 5G) services market friction between neutral host
    providers, virtual operators and operators
    licensing spectrum bands to nations' governments;
    guarantee transparency to consumers,
    and provide a fully GDPR compliant
    schema using a self-sovereign identity system.
  \end{center}
\end{abstract}

@@

Dnsmasq\cite{dnsmasq} was used
as dynamic host configuration server for the wireless
network and
iptables\cite{iptables} was used as a firewall running
both inside the Raspberry; by default, iptables
was configured to
drop all packet
forwarding traffic from users connected to the wireless
domain and at the same time to redirect all
traffic to Raspberry's HTTP port where a
captive portal was listening incoming connections.

\section{Further steps}

\end{multicols}
\begin{center}
%\begin{figure}[h]
  %  \centering
  \includegraphics[keepaspectratio, width=0.8\textwidth]{images/bc5g/bc5g-y.eps}
  \includegraphics[keepaspectratio, width=0.8\textwidth]{images/bc5g/bc5g2-y.eps}
%  \caption{Figura 2. Raspberry Pi 3 Modelo B. Fuente: [Raspberry 18]}
%\end{figure}
\\
Figure 3. Anonymicity, identity, KyC and GDPR.
\\
\end{center}
\begin{multicols}{2}

\end{multicols}
\begin{center}
%\begin{figure}[h]
  %  \centering
  \includegraphics[keepaspectratio, width=0.8\textwidth]{images/bc5g/slices-y.eps}
%  \caption{Figura 2. Raspberry Pi 3 Modelo B. Fuente: [Raspberry 18]}
%\end{figure}
\\
Figure 4. Slicing model.
\\
\end{center}
\begin{multicols}{2}

\end{multicols}
\begin{center}
%\begin{figure}[h]
  %  \centering
  \includegraphics[keepaspectratio, width=0.6\textwidth]{images/bc5g/sc1-y.eps}
  \includegraphics[keepaspectratio, width=0.6\textwidth]{images/bc5g/sc2-y.eps}
  \includegraphics[keepaspectratio, width=0.6\textwidth]{images/bc5g/sc3-y.eps}
%  \caption{Figura 2. Raspberry Pi 3 Modelo B. Fuente: [Raspberry 18]}
%\end{figure}
\\
Figure 5. State channels support instant portability
between different operators with minimal fee.
\\
\end{center}
\begin{multicols}{2}

\end{multicols}
\begin{center}
%\begin{figure}[h]
  %  \centering
  \includegraphics[keepaspectratio, width=0.8\textwidth]{images/bc5g/beyond-y.eps}
%  \caption{Figura 2. Raspberry Pi 3 Modelo B. Fuente: [Raspberry 18]}
%\end{figure}
\\
Figure 6. Full tokenization of wireless services from
the spectrum licensing to the citizen.
\\
\end{center}
\begin{multicols}{2}

%% Un resumen de sus especificaciones se da a continuación (véase tabla 1):
%% \begin{center}
%% %\begin{tabular} to 0.5\textwidth { | X[l] | X[r] | }
%% \begin{tabular}{ | m{0.125\textwidth} | m{0.3125\textwidth} | }
%%  \hline
%%  Especificaciones & Raspberry Pi 3 Modelo B \\
%%  \hline
%%  Procesador & Broadcom BCM2837, Cortex-A53 (ARMv8) 64-bit SoC @ 1,2 GHz \\
%% \hline
%%  RAM & 1 GB \\
%% \hline
%%  Conectividad & Wi-Fi 802.11 b/g/n (2,4 GHz) Bluetooth 4.1 Puerto Ethernet de hasta 100 Mbps \\
%% \hline
%%  Puertos & HDMI completo, 4 USB 2.0, MicroSD, CSI camera, DSI display \\
%% \hline
%%  Memoria & MicroSD \\
%% \hline
%% \end{tabular}
%% \newline
%% \end{center}
%% Tabla 1. Especificaciones de Raspberry Pi 3 Modelo B
%% %\newline
%% Aunque no se indica expresamente si es hardware libre (\textit{open hardware}) o con derechos de marca, en su página Web oficial explican que disponen de contratos de distribución y venta con dos empresas. Pero al mismo tiempo, cualquiera puede convertirse en revendedor o redistribuidor de las tarjetas Raspberry Pi [RaspberryPiBuy 19].
